Quantifying Heterogeneity in SAR Imagery with the Rényi Entropy

### 2025-06-03 Text/Articles/RENYI_ENTROPY_SAR_2025/R1-Renyi-entropy-sar.qmd
Update R1-Renyi-entropy-sar.qmd

```
\textcolor{blue}{
For each SAR image, the number of looks $L$ was obtained from the product of azimuth and range looks provided in the metadata (SNAP). To validate this value, we estimated the equivalent number of looks (ENL) from manually selected homogeneous areas using the classical formula $\text{ENL} = 1/\widehat{\text{CV}}^2$, based on the coefficient of variation. 
The results were consistent with the metadata. We also verified that moderate deviations in $L$ did not significantly impact the outcome of the test, confirming the robustness of the proposed method.}

@@

The output consists of $p$-value maps and binary maps at a $0.05$ significance level. 
The $p$-value maps use a color gradient (Figs.&nbsp;\ref{fig:london-renyi},&nbsp;\ref{fig:london-shann},&nbsp;\ref{fig:munich-renyi},&nbsp;\ref{fig:munich-shann},&nbsp;\ref{fig:dublin-renyi},&nbsp;\ref{fig:dublin-shann}), where darker regions indicate areas with higher roughness, and lighter regions denote smoother, less textured surfaces. 
The binary maps (Figs.&nbsp;\ref{fig:london-005-renyi},&nbsp;\ref{fig:london-005-shann},&nbsp;\ref{fig:munich-005-renyi},&nbsp;\ref{fig:munich-005-shann},&nbsp;\ref{fig:dublin-005-renyi},&nbsp;\ref{fig:dublin-005-shann}) display heterogeneous detections in black ($p<0.05$) and homogeneous areas in white ($p \geq 0.05$).
Visually, the Rényi test exhibits greater sensitivity in detecting textural variations due to the flexibility provided by the parameter $\lambda$.

```{=latex}
\begin{figure*}[hbt]
    \centering
    \begin{subfigure}{0.145\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/london_roi.png}
        \caption{SAR image}
        \label{fig:london-sar}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.142\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/london_optical.png}
        \caption{Optical image}
        \label{fig:london-optical}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.179\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-london_E.png}
        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:london-renyi}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.145\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_renyi_L1_.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:london-005-renyi}
    \end{subfigure}
   \hspace{0.00001\textwidth}
    \begin{subfigure}{0.18\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-london_E.png}
        \caption{$p$-value map for $\tiny{S_{\widetilde{H}_{\text{AO}}}}$ }
        \label{fig:london-shann}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.145\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_shannon.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:london-005-shann}
    \end{subfigure}
    \caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
    \label{fig:london}
\end{figure*}
```

>>>>

```
\textcolor{blue}{
For each SAR image, the number of looks $L$ was obtained from the product of azimuth and range looks provided in the metadata (SNAP). 
We validated this nominal value with the equivalent number of looks (ENL) from manually selected homogeneous areas using the classical formula $\text{ENL} = 1/\widehat{\text{CV}}^2$, based on the sample coefficient of variation. 
The results were consistent with the metadata. 
We also verified that moderate deviations in $L$ did not significantly impact the outcome of the test, confirming the robustness of the proposed method.}

@@

The output consists of $p$-value maps and binary maps at a $0.05$ significance level. 
The $p$-value maps use a color gradient (Figs.&nbsp;\ref{fig:london-renyi},&nbsp;\ref{fig:london-shann},&nbsp;\ref{fig:munich-renyi},&nbsp;\ref{fig:munich-shann},&nbsp;\ref{fig:dublin-renyi},&nbsp;\ref{fig:dublin-shann}), where darker regions indicate areas with higher roughness, and lighter regions denote less textured surfaces. 
The binary maps (Figs.&nbsp;\ref{fig:london-005-renyi},&nbsp;\ref{fig:london-005-shann},&nbsp;\ref{fig:munich-005-renyi},&nbsp;\ref{fig:munich-005-shann},&nbsp;\ref{fig:dublin-005-renyi},&nbsp;\ref{fig:dublin-005-shann}) display heterogeneous detections in black ($p<0.05$) and homogeneous areas in white ($p \geq 0.05$).
Visually, the Rényi test exhibits greater sensitivity in detecting textural variations due to the flexibility provided by the parameter $\lambda$.

<!-- ACF Why three different colour tables? -->
```{=latex}
\begin{figure*}[hbt]
    \centering
    \begin{subfigure}{0.145\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/london_roi.png}
        \caption{SAR image}
        \label{fig:london-sar}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.142\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/london_optical.png}
        \caption{Optical image}
        \label{fig:london-optical}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.179\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_renyi-london_E.png}
        \caption{$p$-value map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:london-renyi}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.145\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_renyi_L1_.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\lambda}}}$}
        \label{fig:london-005-renyi}
    \end{subfigure}
   \hspace{0.00001\textwidth}
    \begin{subfigure}{0.18\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/p-values_shannon-london_E.png}
        \caption{$p$-value map for $\tiny{S_{\widetilde{H}_{\text{AO}}}}$ }
        \label{fig:london-shann}
    \end{subfigure}
    \hspace{0.00001\textwidth}
    \begin{subfigure}{0.145\textwidth}
        \includegraphics[width=\linewidth]{./Figures-R1/H_005_london_shannon.png}
        \caption{Binary map for $\small{S_{\widetilde{H}_{\text{AO}}}}$}
        \label{fig:london-005-shann}
    \end{subfigure}
    \caption{Detection of heterogeneous areas in a SAR image over London, UK: comparison with the tests $\small{S_{\widetilde{H}_{\lambda}}}$ and $\small{S_{\widetilde{H}_{\text{AO}}}}$.}
    \label{fig:london}
\end{figure*}
```
